
\chapter{The LHC Higgs Boson Search}

\section{H $\rightarrow$ ZZ $\rightarrow l^{+}l^{-} \Pq \Paq$ Channel}
In the high mass region for a Higgs boson discovery ($m_{H} > 200 GeV$) the predominant Higgs decay is to vector boson pairs, H $\rightarrow$ WW and H $\rightarrow$ ZZ.  The signatures from the fully leptonic decay modes for these two processes are easily re-constructable and can be distinguished from the background processes.  The fully leptonic decay modes are H $\rightarrow$ WW $\rightarrow$ $l^{+} \Pgn l^{-} \Pagn$ and H $\rightarrow$ ZZ $\rightarrow$ $l^{+}l^{-}l^{+}l^{-}$. The H $\rightarrow$ ZZ $\rightarrow$ $l^{+}l^{-}l^{+}l^{-}$ channel is particularly interesting because the decay chain can be fully reconstructed with a narrow invariant mass peak and almost no Standard Model background. The rate of decay of Z $\rightarrow$ $l^{+}l^{-}$ is only 3.37\% \cite{PDG2012} so for $ l = e,\Pgm$ there is only a 0.45\% chance of ZZ $\rightarrow$ $l^{+}l^{-}l^{+}l^{-}$.

The branching ratio of Z $\rightarrow \Pq \Paq$ is 69.9\% \cite{PDG2012}, and has the largest branching ratio of any Z decay mode. Furthermore, ZZ $\rightarrow \Pq \Paq \Pq \Paq$ has a decay mode of just under 50\%. The problem is that while this maximizes the branching ratio, this final state is indistinguishable from Standard Model background processes, like QCD.

The semi-leptonic final state in H $\rightarrow$ ZZ $\rightarrow l^{+}l^{-} \Pq \Paq$ produces a number of benefits over the previous two decay channels.  The branching ratio of ZZ $\rightarrow l^{+}l^{-} \Pq \Paq$ is 9.4\%, or more than 20 times as large as ZZ $\rightarrow$ $l^{+}l^{-}l^{+}l^{-}$.  In comparison to ZZ $\rightarrow \Pq \Paq \Pq \Paq$ the leptonic decay of one of the Z bosons significantly reduces the Standard Model background in the final state.

Some of the difficulties in this channel compared to the fully leptonic decay are increased difficulty in event selection, the final reconstruction efficiency is approximately half of the fully leptonic final state, the backgrounds are significantly higher and dominated by Z+jets final states, and the resolution is worse.  Despite these difficulties, this channel has improved sensitivity over the fully leptonic final state at high masses because of the higher branching ratio that the semi-leptonic final state enjoys and at high masses the Z+jets background is not as significant.

\section{Background Processes}

The background processes for this channel are processes which have a pair of opposite signed leptons with high transverse momentum that are associated with two jets.  The main backgrounds are listed in Table~\ref{tab:background_2l2q}.

\begin{table}[htb]
\caption{%
  The main Standard Model background processes for the H $\rightarrow$ ZZ $\rightarrow l^{+}l^{-} \Pq \Paq$ channel and their cross sections at 8 TeV.
}
\begin{center}
  \begin{tabular}{ | c | c |} \hline
    Background Process & Cross Section [pb] at 8 TeV\\ \hline \hline
    $\PZ + jets$ & 3503.71 \\ \hline
    $\Pqt \Paqt$ & 225.197\\ \hline
  %  $\Pqt \PWm$  & \\ \hline
  %  $\Paqt \PWp$ & \\ \hline
    $\PZ \PZ$    & 17.654 \\ \hline
    $\PW \PZ$    & 22.88 \\ \hline
    $\PW \PW$    & 57.1097\\ \hline
  \end{tabular}
\end{center}
\label{tab:background_2l2q}
\end{table}

The dominant background in the  $\PH \rightarrow \PZ\PZ \rightarrow l^{+}l^{-} \Pq \Paq$ analysis is the Z+jets background, or more specifically, the inclusive $\PZ$ production with QCD jets.  The cross section of Z production at the LHC is more than 10$^{4}$ larger than the Higgs signal.

Events containing top quarks are another significant source of background.  There are two top processes that result in the same final state as the signal we are studying.  They include $\Pqt \Paqt$ pair production and top quark associated production with a $\PW$ boson.
\begin{center}
  \begin{tabular}{ c }
    $\Pqt \Paqt  \rightarrow (\PWp \rightarrow \Plp\Pgn)\Pqb (\PWm \rightarrow \Plm\Pagn)\Paqb           $
  \end{tabular}
\end{center}

